Exploring Disparate Data: Part 1

### 2024-11-04 A3-Pt1.Rmd
Update A3-Pt1.Rmd
finished all tests passed

-   Aditya (169027493)
-   Andy
-   Dibu
-   Oscar
-   Taras

@@

```{r happiness}
happiness <- read.xlsx("DataForTable2.1.xlsx") |>
    # YOUR CODE HERE

>>>>

-   Aditya (169027493)
-   Andy
-   Dibu
-   Oscar (169057882)
-   Taras

@@

```{r happiness}
happiness <- read.xlsx("DataForTable2.1.xlsx") |>
  janitor :: clean_names() |> 
  rename(
    country = country_name
  ) |>
  filter(!(is.na(life_ladder)))|>
group_by(country) |>                 
  arrange(country, desc(year)) |>      
  slice(1)
